---
title: "Using recipefinder"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using recipefinder}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(recipefinder)
```


## What is "recipefinder"?

"recipefinder" helps you find recipes based on ingredients you already have at home. It uses a recipe database ("Recipes.csv") included in the package and returns meal suggestions based on what you input.

It is made to:

- Reduce food waste  
- Inspire you with what is already in your fridge  
- Quick meal ideas with limited number of ingredients

## Basic usage 

To show all available recipes from the dataset: 
```{r}
head(recipes_list(), 3)
```

To find recipes based on the ingredients you have:
```{r}
head(find_recipes(
  ingredients = c("chicken", "flour", "pepper"),
  file = system.file("extdata", "Recipes.csv", package = "recipefinder")
), 3)
```

## How it works

- The Recipes.csv file contains the titles of the recipes and full ingredient lists.
- The find_recipes() function matches the input ingredients with the recipes from Recipes.csv file, and outputs the matched titles of the recipes and their full ingredient lists. 
